He-Man: A domain-specific language for lightweight concurrency

### 2012-03-06 paper/paper.tex
Update the blocking network call example

\begin{figure}[ht]
\centering
\begin{smallverbatim}
do_nb_action :: Expr -> Prog Expr -> Prog Expr
do_nb_action e action = do
  res <- action
  ifthen (res .< 0) $ do
    while (res .< 0) $ do
      wait e
      res .=. action
  return res

accept (fd, e) =
  do_nb_action e (sock_accept fd)
do_read (fd, e) buf size =
  do_nb_action e (sock_read fd buf size)
do_write (fd, e) buf size =
  do_nb_action e (sock_write fd buf size)
\end{smallverbatim}
\caption{Implementation of ``blocking'' network calls.}
\label{fig:generic}
\end{figure}

>>>>

\begin{figure}[ht]
\centering
\begin{smallverbatim}
do_nb_action :: IntE -> EventE -> Prog IntE -> Prog IntE
do_nb_action mode e action = do
  res <- var "result" Int (-1)
  while (res .< 0) $ do
    set_nb_event_mode e mode
    wait e
    res .=. action
  return res

accept (fd, e) =
  mk_fd <$> do_nb_action kEVENT_RD e (sock_accept fd)
do_read (fd, e) buf size =
  do_nb_action kEVENT_RD e (sock_read fd buf size)
do_write (fd, e) buf size =
  do_nb_action kEVENT_WR e (sock_write fd buf size)
\end{smallverbatim}
\caption{Implementation of ``blocking'' network calls.}
\label{fig:generic}
\end{figure}
